Big Brother Is Watching

### 2015-11-05 manuscript.tex
a

To simplify things, select some time step such that the drone can survey exactly one grid point per time step. Then, if either $m$ or $n$ is even, the amount of time it takes is just $m*n$. Proof: The proof is visual

@@

>>>>

To simplify things, select some time step such that the drone can survey exactly one grid point per time step. Then, if either $m$ or $n$ is even, the amount of time it takes is just $m*n$. Proof: See Figure \ref{path} in section 4, and note that the number of "zigzags" is even and the path does not cross over itself. However, if neither is even, we may not be able to traverse the rectangle and return to the starting position in $m*n$ steps. Instead, we can traverse the rectangle in a similar zigzag pattern (with the long edge of the zigzags perpendicular to the longer edge of the rectangle), and then at the end of the last zigzag (which will end in the middle of the rectangle instead of at the starting corner), move towards the starting corner, which will take $min(m,n) - 1$ time (see Figure \ref{path2}). The exception to both cases is if either $m$ or $n$ is 1. Assume WLOG that $m = 1$; in this case, it will take $2n - 1$ time to traverse all the grid points and return to the starting position, since once we traverse all the grid points (say, from "left to right"), which takes $n - 1$ steps, we will have to retrace our steps, which takes $n-1$ more steps.

\begin{figure}[htb!]
    \centering{{\includegraphics[width=7cm]{figures/odd_path.pdf} }}
    \caption{The shape of a path in a rectangle with an odd height and odd width. The path begins in the top right corner and goes to the left, and reverses directions from downward to upward when it gets to the bottom right corner.}
    \label{path2}
\end{figure}

Using this formula, we are ready to find the optimal arrangement of rectangular blocks that covers Manhattan while using the fewest drones.

@@

This method can be extended to the case where some areas must be observed more often than others. We can just assume that these areas are rectangular (which is a fairly good assumption in this case) and treat these areas as separate blocks.
